Analyses

### 2022-04-11 analyses.RmD
- deleted data

```{r knitr-setup, include=F}
set.seed(170819)
knitr::opts_chunk$set(warning=F, echo=T, error=F, message=F, cache = T)
options(digits = 3, width = 250, scipen=999)
```

@@

# define packages
packages <- c("brms", "devtools", "GGally", "ggplot2", 
              "gridExtra", "kableExtra", "knitr", "lavaan", "lme4", 
              "magrittr", "mice", "mvnormalTest", 
              "PerFit", "psych", "quanteda.textstats", "semTools", "tidyverse")

@@

@@

@@

@@

@@

@@

@@

```{r}
# get data
get_dat_res <- function(data_aff_neg, data_aff_pos, data_life_sat, type){

  dat_fig_results <- 
  broom.mixed::tidy(data_aff_neg, conf.int = T) %>% 
  mutate(dv = "aff_neg") %>% 
  rbind(
    broom.mixed::tidy(data_aff_pos, conf.int = T) %>% 
    mutate(dv = "aff_pos")
  ) %>% 
  rbind(
    broom.mixed::tidy(data_life_sat, conf.int = T) %>% 
    mutate(dv = "life_sat")
  ) %>% 
  mutate(
    type = ifelse(grepl(".*_w\\>", .$term), "within", "between"),
    iv = gsub("_(w|b)\\>", "", .$term)
         ) %>%
  mutate(
    type = factor(.$type, 
                  levels = c("within", "between")),
    dv = factor(.$dv, 
                levels = c("life_sat", "aff_pos", "aff_neg"),
                labels = c("Life satisfaction", "Positive affect", "Negative affect"))
  ) %>% 
  select(dv, iv, type, estimate, conf.low, conf.high, p.value)

  # select Social Media type of activity
  if(type == "activity") {
    dat_fig_results %<>%
    filter(iv %in% c("soc_med_read", "soc_med_like_share", "soc_med_post")) %>% 
    mutate(
      iv = factor(.$iv, 
                  levels = c("soc_med_post", "soc_med_like_share", "soc_med_read"), 
                  labels = c("Posting", "Liking & Sharing", "Reading"))
    )
  } else if(type == "channel"){
    dat_fig_results %<>%
    filter(iv %in% c("soc_med_fb", "soc_med_ig", "soc_med_wa", "soc_med_yt", "soc_med_tw")) %>% 
    mutate(iv = factor(.$iv, levels = c("soc_med_yt", "soc_med_wa", "soc_med_ig", "soc_med_tw", "soc_med_fb"), labels = c("YouTube", "WhatsApp", "Instagram", "Twitter", "Facebook")))
  } else if(type == "control"){
    dat_fig_results %<>%
      filter(iv %in% c("male", "health", "loc_cntrl_int_m", "employment_facPublic service", "act_spo", "sat_dem")) %>% 
      mutate(iv = factor(.$iv, levels = c("male", "health", "loc_cntrl_int_m", "employment_facPublic service", "act_spo", "sat_dem"), 
                         labels = c("Male", "Health", "Internal locus of control", "Employed public service", "Sport", "Satisfaction democracy")))
  }
  return(dat_fig_results)
}

@@

@@

```{r}
make_graph_res <- function(data_1, data_2 = NULL, sesoi = NULL){
  ggplot(data_1, aes(x = estimate, y = iv)) + 
  scale_color_manual(values = c("grey40", "deepskyblue")) +
  geom_vline(xintercept = 0, lwd = .75, colour = "darkgrey") + 
  geom_errorbarh(aes(xmin = conf.low, xmax = conf.high),
                lwd = .75, height = .2) +
  geom_point(size = 2) +
  {if(!is.null(data_2)) geom_errorbarh(aes(xmin = conf.low, xmax = conf.high), data_2,
                lwd = .75, height = .2, color = "grey",
                position = position_nudge(y = -.3)
                )} +
  {if(!is.null(data_2)) geom_point(data = data_2, size = 2, color = "grey",
             position = position_nudge(y = -.3)
             )} +
  {if(isTRUE(sesoi == "est")) geom_vline(data=filter(data_1, dv=="Life satisfaction"), aes(xintercept=-.3), colour="darkgrey", linetype = "dashed")} + 
    {if(isTRUE(sesoi == "est")) geom_vline(data=filter(data_1, dv=="Life satisfaction"), aes(xintercept=.3), colour="darkgrey", linetype = "dashed")} + 
  {if(isTRUE(sesoi == "est")) geom_vline(data=filter(data_1, dv!="Life satisfaction"), aes(xintercept=-.15), colour="darkgrey", linetype = "dashed")} +
    {if(isTRUE(sesoi == "est")) geom_vline(data=filter(data_1, dv!="Life satisfaction"), aes(xintercept=.15), colour="darkgrey", linetype = "dashed")} +
  {if(isTRUE(sesoi == "std")) geom_vline(aes(xintercept=.1), colour="darkgrey", linetype = "dashed")} + 
  {if(isTRUE(sesoi == "std")) geom_vline(aes(xintercept=-.1), colour="darkgrey", linetype = "dashed")} +   theme(
    axis.title.y = element_blank(),
    plot.title = element_text(hjust = .5),
    panel.spacing = unit(.9, "lines"),
    text = element_text(size = 12),
    axis.text.y = element_text(hjust = 0)
    ) +
  facet_grid(rows = vars(type),
             cols = vars(dv),
             scales = "free",
             space = "free_y") 
}
```

@@

```{r eval=TRUE}
vars_used <- c("life_sat", "aff_pos_1", "aff_pos_2", "aff_pos_3", "aff_neg_1", "aff_neg_2", "aff_neg_3", "aff_neg_4", "aff_neg_5", "aff_neg_6", "soc_med_read", "soc_med_like_share", "soc_med_post", "soc_med_fb", "soc_med_ig", "soc_med_wa", "soc_med_yt", "soc_med_tw", "age", "male", "born_aus", "born_aus_prnts", "edu_fac", "employment_fac", "health", "res_vienna", "acc_bal", "acc_gar", "home_sqm", "med_txt_kro", "med_txt_sta", "med_txt_pre", "med_txt_oes", "med_txt_kur", "med_txt_slz", "med_txt_son", "med_vid_orf", "med_vid_pri", "risk_prop", "loc_cntrl_int_1", "loc_cntrl_int_2", "loc_cntrl_int_3", "loc_cntrl_int_4", "act_wrk", "act_spo", "act_frn", "act_sho", "act_pet", "sat_dem")

@@

# init <- mice(select(d_long_test_filt, maxit = 0))
# pred_ma <- init$predictorMatrix
# pred_ma[, vars_excl] <- 0
d_long_imp <- mice(d_long_filt, method = "pmm", m = 1, maxit = 30, 
              where = incl_ma,
              # predictorMatrix = pred_ma, 
              seed = 180719, print = FALSE)
d_long_imp <- mice::complete(d_long_imp)

write_csv(d_long_imp, "data/data_imputed.csv")
```

@@

@@

@@

```{r}
# get data
dat_fig_results_activity <- get_dat_res(model_aff_neg_lmer, model_aff_pos_lmer, model_life_sat_lmer, type = "activity")
dat_fig_results_activity_nco <- get_dat_res(model_aff_neg_lmer_nco, model_aff_pos_lmer_nco, model_life_sat_lmer_nco, type = "activity")

# make figure
fig_results_activity <- make_graph_res(
  data_1 = dat_fig_results_activity,
  data_2 = dat_fig_results_activity_nco,
  sesoi = "est"
  )
fig_results_activity

@@

```{r}
# get data
dat_fig_results_channel <- get_dat_res(model_aff_neg_lmer, model_aff_pos_lmer, model_life_sat_lmer, type = "channel")
dat_fig_results_channel_nco <- get_dat_res(model_aff_neg_lmer_nco, model_aff_pos_lmer_nco, model_life_sat_lmer_nco, type = "channel")

# make figure
fig_results_channel <- make_graph_res(
  data_1 = dat_fig_results_channel,
  data_2 = dat_fig_results_channel_nco,
  sesoi = "est"
  )
fig_results_channel

# save figure
ggsave("figures/fig_results_channel.pdf", 
       width = 7, height = 4,
       plot = fig_results_channel)
```

@@

```{r}
# make figure
fig_results_control <- make_graph_res(
  get_dat_res(model_aff_neg_lmer, model_aff_pos_lmer, model_life_sat_lmer, type = "control")
  )
fig_results_control

>>>>

```{r knitr-setup, include=F}
set.seed(170819)
knitr::opts_chunk$set(warning=F, echo=T, error=F, message=F, cache = F)
options(digits = 3, width = 250, scipen=999)
```

@@

# define packages
packages <- c("broom.mixed", "brms", "devtools", "GGally", "ggplot2", 
              "gridExtra", "kableExtra", "knitr", "lavaan", "lme4", 
              "magrittr", "mice", #"mvnormalTest", 
              "PerFit", "psych", "quanteda.textstats", "semTools", "tidyverse")

@@

### find_var

@@

### get_specs

@@

### get_dat

@@

### get_rel

@@

### make_graph

@@

### get_dat_res

@@

```{r}
# get data
get_dat_res <- function(data_aff_neg, data_aff_pos, data_life_sat, type, analysis = NULL){

  if(isTRUE(class(data_aff_neg) == "lmerModLmerTest")) {
         dat_fig_results <- 
           broom.mixed::tidy(data_aff_neg, conf.int = T) %>% 
           mutate(dv = "aff_neg") %>% 
           rbind(
             broom.mixed::tidy(data_aff_pos, conf.int = T) %>% 
               mutate(dv = "aff_pos")) %>% 
           rbind(
             broom.mixed::tidy(data_life_sat, conf.int = T) %>% 
               mutate(dv = "life_sat"))
         } else{ 
           dat_fig_results <- 
             data_aff_neg %>% 
             mutate(dv = "aff_neg") %>% 
             rbind(data_aff_pos %>% 
                   mutate(dv = "aff_pos")) %>% 
             rbind(data_life_sat %>% 
                     mutate(dv = "life_sat")) %>% 
           rename(conf.low = `2.5 %`, conf.high = `97.5 %`)
           }
  dat_fig_results %<>% 
  mutate(
    type = ifelse(grepl(".*_w\\>", .$term), "within", "between"),
    iv = gsub("_(w|b)\\>", "", .$term)
         ) %>%
  mutate(
    type = factor(.$type, 
                  levels = c("within", "between")),
    dv = factor(.$dv, 
                levels = c("life_sat", "aff_pos", "aff_neg"),
                labels = c("Life satisfaction", "Positive affect", "Negative affect")),
    analysis = analysis
  ) %>% 
  select(dv, iv, type, analysis, estimate, conf.low, conf.high, p.value)

  # select Social Media type of activity
  if(type == "activity") {
    dat_fig_results %<>%
    filter(iv %in% c("soc_med_read", "soc_med_like_share", "soc_med_post")) %>% 
    mutate(
      iv = factor(.$iv, 
                  levels = c("soc_med_post", "soc_med_like_share", "soc_med_read"), 
                  labels = c("Posting", "Liking & Sharing", "Reading"))
    )
  } else if(type == "channels"){
    dat_fig_results %<>%
    filter(iv %in% c("soc_med_fb", "soc_med_ig", "soc_med_wa", "soc_med_yt", "soc_med_tw")) %>% 
    mutate(iv = factor(.$iv, levels = c("soc_med_yt", "soc_med_wa", "soc_med_ig", "soc_med_tw", "soc_med_fb"), labels = c("YouTube", "WhatsApp", "Instagram", "Twitter", "Facebook")))
  } else if(type == "control"){
    dat_fig_results %<>%
      filter(iv %in% c("male", "health", "loc_cntrl_int_m", "employment_facPublic service", "act_spo", "sat_dem")) %>% 
      mutate(iv = factor(.$iv, levels = c("male", "health", "loc_cntrl_int_m", "employment_facPublic service", "act_spo", "sat_dem"), 
                         labels = c("Male", "Health", "Internal locus of control", "Employed public service", "Sport", "Satisfaction democracy")))
  }
  return(dat_fig_results)
}

@@

### make_graph_res

@@

```{r}
make_graph_res <- function(data, sesoi = NULL, legend = TRUE){
  ggplot(data, aes(x = estimate, y = iv)) + 
  scale_color_manual(values = c("grey40", "deepskyblue", "darkcyan", "cornflowerblue", "aquamarine")) +
  geom_vline(xintercept = 0, lwd = .75, colour = "darkgrey") + 
  geom_errorbarh(aes(xmin = conf.low, xmax = conf.high, color = analysis),
                lwd = .75, height = .2, position = position_dodge(.5)) +
  geom_point(aes(color = analysis), size = 2, position = position_dodge(.5)) +
  {if(isTRUE(sesoi == "est")) geom_vline(data=filter(data, dv=="Life satisfaction"), aes(xintercept=-.3), colour="darkgrey", linetype = "dashed")} + 
    {if(isTRUE(sesoi == "est")) geom_vline(data=filter(data, dv=="Life satisfaction"), aes(xintercept=.3), colour="darkgrey", linetype = "dashed")} + 
  {if(isTRUE(sesoi == "est")) geom_vline(data=filter(data, dv!="Life satisfaction"), aes(xintercept=-.15), colour="darkgrey", linetype = "dashed")} +
    {if(isTRUE(sesoi == "est")) geom_vline(data=filter(data, dv!="Life satisfaction"), aes(xintercept=.15), colour="darkgrey", linetype = "dashed")} +
  {if(isTRUE(sesoi == "std")) geom_vline(aes(xintercept=.1), colour="darkgrey", linetype = "dashed")} + 
  {if(isTRUE(sesoi == "std")) geom_vline(aes(xintercept=-.1), colour="darkgrey", linetype = "dashed")} +   
    theme(
    axis.title.y = element_blank(),
    plot.title = element_text(hjust = .5),
    panel.spacing = unit(.9, "lines"),
    text = element_text(size = 12),
    axis.text.y = element_text(hjust = 0)
    ) +
  {if(!isTRUE(legend)) theme(legend.position = "none")} + 
  guides(colour = guide_legend(reverse=T)) +
  facet_grid(rows = vars(type),
             cols = vars(dv),
             scales = "free",
             space = "free_y") 
}
```

### get_fs

@@

```{r eval=TRUE, cache=TRUE}
vars_used <- c("life_sat", "aff_pos_1", "aff_pos_2", "aff_pos_3", "aff_neg_1", "aff_neg_2", "aff_neg_3", "aff_neg_4", "aff_neg_5", "aff_neg_6", "soc_med_read", "soc_med_like_share", "soc_med_post", "soc_med_fb", "soc_med_ig", "soc_med_wa", "soc_med_yt", "soc_med_tw", "age", "male", "born_aus", "born_aus_prnts", "edu_fac", "employment_fac", "health", "res_vienna", "acc_bal", "acc_gar", "home_sqm", "med_txt_kro", "med_txt_sta", "med_txt_pre", "med_txt_oes", "med_txt_kur", "med_txt_slz", "med_txt_son", "med_vid_orf", "med_vid_pri", "risk_prop", "loc_cntrl_int_1", "loc_cntrl_int_2", "loc_cntrl_int_3", "loc_cntrl_int_4", "act_wrk", "act_spo", "act_frn", "act_sho", "act_pet", "sat_dem")

@@

d_long_imp <- mice(d_long_filt, 
                   method = "pmm", # use predictive mean matching
                   m = 1, maxit = 30, # only 1 imputation
                   where = incl_ma,
                   seed = 180719, print = FALSE)
d_long_imp <- mice::complete(d_long_imp)
write_csv(d_long_imp, "data/data_imputed.csv")
```

```{r eval=TRUE, cache=TRUE}
# impute missing data with multiple imputation
d_long_mim_mice <- mice(d_long_filt, 
                   method = "pmm", # use predictive mean matching
                   m = 5, maxit = 5, # 5 imputations, 5 iterations
                   where = incl_ma,
                   seed = 180719, print = FALSE)
d_long_mim <- mice::complete(d_long_mim_mice, action = "long", include = TRUE)
```

@@

And now the same for the multiple imputed data

```{r}
d_long_mim %<>%
  mutate(aff_pos_m = rowMeans(select(., aff_pos_1 : aff_pos_3)),
         aff_neg_m = rowMeans(select(., aff_neg_1 : aff_neg_6)),
         loc_cntrl_int_m = rowMeans(select(., loc_cntrl_int_1 : loc_cntrl_int_4)))

d_long_mim %<>% 
  group_by(id) %>% 
  mutate_at(vars(health:loc_cntrl_int_4, loc_cntrl_int_m), funs(b = mean(., na.rm = TRUE), w = . - mean(., na.rm = TRUE))) %>% 
  ungroup()

d_long_mim_mice <- as.mids(d_long_mim)
```

@@

Assumption of multivariate normal distribution was violated; hence, robust estimator will be used.

@@

```{r}
# get data
dat_fig_results_activity <- get_dat_res(model_aff_neg_lmer, model_aff_pos_lmer, model_life_sat_lmer, 
                                        type = "activity", analysis = "regular")
dat_fig_results_activity_nco <- get_dat_res(model_aff_neg_lmer_nco, model_aff_pos_lmer_nco, model_life_sat_lmer_nco, 
                                            type = "activity", analysis = "no controls")
dat_fig_results_activity <- rbind(
  dat_fig_results_activity, 
  dat_fig_results_activity_nco
)

# make figure
fig_results_activity <- make_graph_res(
  data = dat_fig_results_activity,
  sesoi = "est"
  )
fig_results_activity

@@

```{r}
# get data
dat_fig_results_channels <- get_dat_res(model_aff_neg_lmer, model_aff_pos_lmer, model_life_sat_lmer, 
                                        type = "channels", analysis = "regular")
dat_fig_results_channels_nco <- get_dat_res(model_aff_neg_lmer_nco, model_aff_pos_lmer_nco, model_life_sat_lmer_nco, 
                                            type = "channels", analysis = "no controls")
dat_fig_results_channels <- rbind(
  dat_fig_results_channels, 
  dat_fig_results_channels_nco
)

# make figure
fig_results_channels <- make_graph_res(
  data = dat_fig_results_channels,
  sesoi = "est"
  )
fig_results_channels

# safe figure
ggsave("figures/fig_results_channels.pdf", 
       width = 7, height = 4,
       plot = fig_results_channels)
```

@@

```{r}
# make figure
fig_results_control <- make_graph_res(
  get_dat_res(model_aff_neg_lmer, model_aff_pos_lmer, model_life_sat_lmer, analysis = "exploratory", type = "control"),
  legend = FALSE
  )
fig_results_control
